\documentclass[preprint,nocopyrightspace]{sigplanconf-noauthor}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xspace,url}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{multirow,color}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{alltt}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{listings}
\lstset{
  language=C++,
  basicstyle=\scriptsize\ttfamily,
  % emph={foreach},
  % emphstyle=\textbf,
  morekeywords={size\_t, token\_t},
  numbers=left,
  showstringspaces=false,
  escapechar={@},
  keywordstyle=\color{blue},
  %stringstyle=\color{magenta},
  commentstyle=\color{red},
  morecomment=[s][\color{red}]{[[}{]]}
}
\usepackage{tabularx}

%\usepackage[sort&compress]{natbib}

%\newcommand{\subparagraph}{}
\usepackage[compact]{titlesec}

\newtheorem{theorem}{\noindent {Theorem}}{}
\newtheorem{lemma}{\noindent {Lemma}}{}
\newtheorem{claim}{\noindent {Claim}}{}
\newtheorem{observation}{\noindent {Observation}}{}
\newtheorem{definition}{\noindent {Definition}}
\newtheorem{problem}{\noindent {Problem}}{}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{MyBlue}{rgb}{0.1,0.3,0.75}
\newcommand{\note}[1]{\textcolor{red}{\bf \em #1}}
%\newcommand{\comment}[1]{{\color{gray}[\textsf{#1}]}}
\newcommand{\authorcomment}[1]{\iffalse #1 \fi}
\newcommand{\etc}{\emph{etc.}\xspace}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}
\newcommand{\bfem}{\bf \em}

\newcommand{\vrisha}{{\sc Vrisha}\xspace}
\newcommand{\wukong}{{\sc WuKong}\xspace}
\newcommand{\lancet}{{\sc Lancet}\xspace}

\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand\vartextvisiblespace[1][.5em]{%
  \makebox[#1]{%
    \kern.07em
    \vrule height.3ex
    \hrulefill
    \vrule height.3ex
    \kern.07em
  }% <-- don't forget this one!
}

%caption for table
%\newcommand{\mtcaption}[1]{\caption{#1}\vspace{-0.1in}}
%\newcommand{\mfcaption}[1]{\vspace{-0.03in}\caption{#1}\vspace{-0.25in}}
%\newenvironment{mytable}{\begin{table}}{\vspace{-0.15in}\end{table}}
%\newenvironment{mytable*}{\begin{table*}}{\vspace{-0.15in}\end{table*}}

% TODO: it would be nice to not have to do this
%\linespread{0.972}

\begin{document}

\authorpermission

%\titlebanner{banner above paper title}        % These are ignored unless
%\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Efficient Load Test Generation}

\authorinfo{Bowen Zhou \and Milind Kulkarni \and Saurabh Bagchi}
           {Purdue University}
           {\{bzhou, milind, sbagchi\}@purdue.edu}

\maketitle

\pagenumbering{arabic}
\pagestyle{plain}

\begin{abstract}

A crucial part of any software testing regimen is {\em performance testing}:
a program must be put under load, \eg by executing a critical loop of the program many times, to
ensure that the program behaves as expected at large scales. Unfortunately,
generating precise performance tests, where a specific part of the program can be 
exercised at a controllable load level, is challenging. The standard approach to generating
performance tests using dynamic symbolic execution incurs too much overhead to
effectively generate large-scale test inputs. We propose \lancet, a dynamic
symbolic execution--based tool that sidesteps the overheads. \lancet has two
key innovations: (i) a path exploration heuristic for dynamic symbolic
execution that more effectively generates scaling inputs for loops in complex
programs; and (ii) a novel {\em constraint inference} method, that uses
statistical inference on small-scale inputs to automatically infer constraints
that describe large-scale inputs, allowing programmers to generate
large inputs without performing symbolic execution at large scales. We
demonstrate the effectiveness of \lancet by using it to infer large-scale,
targeted inputs for synthetic benchmarks and real-world distributed applications
such as Memached and Redis.

\end{abstract}

% \category{D.2.4}{Software Engineering}{Software/Program Verification}[Statistical Methods]
% \category{D.2.5}{Software Engineering}{Testing and Debugging}[Diagnostics]
%  
% \terms
% 
% \keywords

\sloppy

\input{sections/intro}
\input{sections/background}
% \input{sections/overview}
\input{sections/method}
%\input{sections/extensions}
%\input{sections/discuss}
\input{sections/prototype}
\input{sections/eval}
\input{sections/relate}
\input{sections/ending}

% \renewcommand{\bibfont}{\scriptsize\raggedright}
\setlength{\bibsep}{2pt}
% \bibliographystyle{abbrvnat}
\bibliographystyle{abbrv}
\bibliography{paper}

%% The bibliography should be embedded for final submission.
%
%\begin{thebibliography}{}
%\softraggedright
%
%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...
%
%\end{thebibliography}

\end{document}
